Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-04 ch04-lrmhinf/lrmhinf.tex
Add epigraphs
Some changes from Tom
Add some TODOs
Different figure names per chapter
Lots of work on LRMHinf + description of AVIS setup
Lots of changes to CH04
Clean up on aisle CH04
Add photo details of AVIS

\chapter{Non-parametric resonance modeling}
\label{sec:hinf}

>>>>

\chapter{Non-parametric Resonance Peak Modeling}
\label{sec:hinf}
\def\thisDir{ch04-lrmhinf}
\tikzsetfigurename{ch04fig}
\myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
\researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
\glsresetall

%TODO: add section from Benchmark paper

\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

% \section{Introduction}
% \label{sec:lrmhinf:Intro}

For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.

Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability.
An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
However, the performance of skyhook damping is limited by high-frequent lightly-damped parasitic resonance phenomena.
Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.

Several approaches have been developed to determine bounds on the model uncertainty. 
First, model validation techniques have been developed~\citep[see e.g.][]{Smith1992,Xu1999}.
However, these results are typically overly optimistic~\citep{Oomen2009UncEstim}.
Second, model error modeling approaches based on parametric system identification~\citep{Ljung1999MEM} with explicit characterization of bias and variance errors have been proposed, but these require a significant amount of user intervention.
Third, non-parametric identification approaches have been adopted, e.g.~\citep{vandeWal2002,deVries1994}. 
In~\citep{vandeWal2002}, an identified frequency response function is used directly to evaluate the \Hinf{} norm on a discrete frequency grid. 
In~\citep{deVries1994}, an extended method is presented that bounds the error in between frequency points in a worst-case fashion. 
However, such worst-case methods are well-known to be overly conservative~\citep[Section 9.5.2]{Vinnicombe2001}. 
Fourth, recently a data-driven \Hinf{} norm estimation has been developed in~\citep{Wahlberg2010,Oomen2014ILH}.
These methods rely on a sequence of iterative experiments and directly delivers an estimate of the \Hinf{} norm, and combines an optimal experiment design while essentially taking inter-grid errors into account.
A recent application of this method in~\citep{Oomen2014ILH} has revealed that these iterative methods lead to significantly more accurate \Hinf{} estimates compared with traditional frequency response-based methods, thereby underlining the importance of the inter-grid error.
Unfortunately, these methods require a sequence of dedicated iterative experiments.
This increases the measurement time significantly, especially for \gls{MIMO} plants.
When measurement time is expensive, this is a severe impediment.

Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM} \citep{Schoukens2009LPM} and \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.

\paragraph*{Outline}
\label{par:lrmhinf:toc}
The problem is formulated in \secref{sec:lrmhinf:Problem}.
In \secref{sec:lrmhinf:LPMHinf} the novel method to estimate the $\Hinf{}$ norm by means of the \gls{LRM} is introduced.
In \secref{sec:lrmhinf:simulation} the method is illustrated on simulations, and the required measurement time is determined.
The technique is demonstrated on measurements of an \gls{AVIS} in \secref{sec:lrmhinf:measurement}.
Finally, the results and some challenges are discussed in \secref{sec:lrmhinf:conclusion}.

%\glsresetall

\section{Problem Formulation}
\label{sec:lrmhinf:Problem}
Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
The \Hinf{} norm of the error system $\Delta$ is
\begin{equation}
  \gamma 
     = 
       \infnorm{\Delta} 
    \isdef 
       \sup_{\omega} 
         \svdMax{\Delta(\omega)}
  \label{eq:lrmhinf:HinfNorm}
\end{equation}
for a stable system where $\svdMax{\placeholder}$ denotes the maximum singular value of $\placeholder$.
Note that for \gls{SISO} systems, $\svdMax{\Delta} = \abs{\Delta}$ and the definition above reduces to
\begin{equation}
  \gamma 
    = 
       \infnorm{\Delta} 
    \isdef 
         \sup_{\omega} 
         \abs{\Delta(\omega)}
  \text{ for \gls{SISO} systems}
  \text{.}
  \label{eq:lrmhinf:HinfNormSISO}
\end{equation}
In robust control design methodologies, such \Hinf{} norms often play an important purpose to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.

\begin{remark}
It is even more common to use a weighted norm $\infnorm{W \Delta V}$ in robust control designs where $(W,V)$ are stable and minimum-phase weighting filters.
Two use cases can be distinguished: either these filters are chosen by the control engineer and hence known, or, one wishes to construct such filters from data.
In the case where the weighting filters are `known', the approach of this chapter can be adapted in a straightforward manner to account for these weights, i.e. by replacing $\svdMax{\Delta}$ with $\svdMax{W \Delta V}$ in the formulas.
The other case is discussed in Remark~\ref{rem:lrmhinf:constructWeights} further on.
\end{remark}

To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
\begin{equation}
 \omega_{\star} 
     \isdef 
       \arg
         \sup_{\omega} 
           \svdMax{\Delta(\omega)}
  \text{.}
  \label{eq:lrmhinf:omega-star}
\end{equation}
However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
\begin{align}
  \gamma &\isdef 
    \sup_{\omega} 
      \svdMax{\Delta(\omega)}
         = \max 
             \Set{
                \max_{\omega \in \DFTGrid  } 
                  \svdMax{\Delta(\omega)}
                \;,\;
                \sup_{\omega \in \InterGrid} 
                  \svdMax{\Delta(\omega)}
                }
  \label{eq:lrmhinf:gamma-split-grid}\\
  \gammaAtGrid & \isdef 
    \max_{\omega \in \DFTGrid  } 
      \svdMax{\Delta(\omega)}
  \label{eq:lrmhinf:gamma:atGrid}\\
  \gammaIntergrid & \isdef 
    \sup_{\omega \in \InterGrid} 
      \svdMax{\Delta(\omega)}
   \label{eq:lrmhinf:gamma:interGrid}
\end{align}
where $\Omega \isdef \OpenInterval{0,\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
Direct inspection of the \gls{FRF} data only allows access to $\gammaAtGrid$.
Two cases can be distinguished:
\begin{enumerate}
  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
\end{enumerate}
The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
Its expected value over different realizations of the input signal $\expectedValue{\gammaAtGrid} \leq \gamma$ due to the limited frequency resolution.
Such an underestimate may lead to overly optimistic controller designs.

The main contribution of this chapter is to  estimate the inter-grid term $\gammaIntergrid$ without the need for a (global) parametric model.
Instead, a  realistic value of $\gamma$ is obtained using parametric models that are valid over small frequency ranges.

\subsection{Set-up}
Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
For an infinitely long data record, this can be described in the time-domain as
\begin{equation}
  y_{\Delta}(n) 
    = 
      y_{\Delta0}(n)
      + v(n) 
    = 
      \Delta(q)u_{\Delta}(n) 
      + H(q)e(n)
  \label{eq:lrmhinf:sysDeltaInfData}
\end{equation}
where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
\begin{equation}
    y_{\Delta}(n) 
      = 
        \Delta(q)u(n) 
        + H(q)e(n) 
        + t_{\Delta}(n)
    \text{.}
    \label{eq:lrmhinf:sysDeltaFiniteData}
\end{equation}
By applying the \gls{DFT}
\begin{equation}
  X(k) 
       = 
         \frac{1}
              {\sqrt{N}} 
         \sum_{n=0}^{N-1} 
            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
         \quad   
         \forall k \in \mathbb{Z}
  \label{eq:lrmhinf:DFT}
\end{equation} 
to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
\begin{equation}
  Y_{\Delta}(k) 
                = 
                  \Delta(\omega_k) U_{\Delta}(k) 
                  + T_{\Delta}(\omega_k) 
                  + V(k) 
  \text{.}
  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
\end{equation}
The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.

The presented results in this paper directly extend to closed-loop systems, as is shown in \secref{sec:lrmhinf:control}.
The results in this chapter are presented in discrete time, but the extension to the continuous time case is straightforward.

\section{\Hinf{} Norm Estimation Procedure}
\label{sec:lrmhinf:LPMHinf}
To estimate $\gammaIntergrid$, we propose to identify local parametric models in the frequency domain.
The frequency axis is partitioned into continuous segments $\Omega_k \isdef \OpenInterval{ \omega_{k-1} , \omega_{k+1} }$ in view of the local validity of the local models.
In particular, the inter-grid aspect of the $\Hinf$ norm is estimated as
\begin{equation}
  \gammaIntergrid = 
    \sup \Set{ 
                \sup_{\omega \in \Omega_k} \svdMax{\LocalModel{\Delta}_k(\omega)}
                |
                k = 1,\ldots,N-1
                }
   \label{eq:lrmhinf:gamma-inter-grid}
\end{equation}
where the $\LocalModel{\Delta}_{k}$ is the local model around the ($k^{\text{th}}$) frequency bin $\omega_k$.
An example of such local models is shown in \figref{fig:lrmhinf:interpol-quantities}.
Two alternative methods allow evaluation of~\eqref{eq:lrmhinf:gamma-inter-grid} in practice.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.68\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/interpolation-show.tikz}
  \caption[Illustration of the local models.]{Illustration of the local models $\LocalModel{\Delta}_k$ around each frequency bin $\omega_k$ for $k\in\Set{1,\ldots,6}$.
  The bottom part shows the equivalence of the frequency segments $\Omega_k$ and the intervals $\Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}$.}
\label{fig:lrmhinf:interpol-quantities}
\end{figure}

\paragraph*{Direct method}
One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
Hence, it boils down to solving the optimization problems
\begin{align}
  \estimated{\gammaIntergrid}(k) & \isdef 
      \sup_{\omega \in \Omega_k}
      \svdMax{\LocalModel{\Delta}_k(\omega)}
       \quad \forall k \in \Set{1,\ldots,N-1} 
       \label{eq:lrmhinf:gamma-direct:optimizations}\\
  \estimated {\gammaIntergrid} &= 
  \max \Set{
    \estimated{\gammaIntergrid}(k) 
    | 
    k \in \Set{1,\ldots,N-1}
  }
      \label{eq:lrmhinf:gamma-direct}
\end{align}
These are tractable since $\omega$ is one-dimensional and restricted to the closed intervals $\Omega_k$.
Unfortunately, this approach offers no insight in the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.

\paragraph{Interpolation method}
To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\svdMax{\omega_k-\omega}$ is small.
To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
\begin{align}
  k_L(\omega) & 
                \isdef
                  \max
                  \Set{
                    k 
                    |
                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
                  }\\
  k_R(\omega) & 
                \isdef
                  \min
                  \Set{
                    k
                    |
                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
                  }
  \text{.}
  \label{eq:lrmhinf:kL-kR-indexing-functions}
\end{align}
Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
\begin{equation*}
 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)} 
 \quad \text{ and } \quad
 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
\end{equation*}
In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
\begin{equation}
  \svdMax{\Delta_{\LMM}(\omega)}
    \isdef
    \max \Set{
       \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
        \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
    }
    \label{eq:lrmhinf:DeltaLRMInterpolation}
\end{equation}
by retaining the largest both.
It follows that
\begin{align}
  \widehat{\infnorm{\Delta_{\LMM}}}
    & \isdef
    \sup_{\omega\in\Omega}
    \svdMax{\Delta_{\LMM}(\omega)} \\
   &  =
      \sup_{\omega\in\Omega} \; 
      \max \Set{
                 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
                 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
  \label{eq:lrmhinf:gammaInterpolOptim}
  \text{.}
\end{align}

\paragraph*{Remarks:}
The optimization problems~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct:optimizations} each amount to one-dimensional optimization problems, hence they be solved easily by griding the frequency $\omega$.
The peak amplitudes obtained using~\eqref{eq:lrmhinf:gammaInterpolOptim} and~\eqref{eq:lrmhinf:gamma-direct} are identical since the local models $\LocalModel{\Delta}_k$ are evaluated over identical frequency ranges
 \begin{equation}
  \Omega_k = \Set{\omega \given{k_L(\omega) = k \vee k_R(\omega) = k}}
 \end{equation}
for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
In \figref{fig:lrmhinf:interpol-quantities} the functions $k_L(\omega)$ and $k_R(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.

\subsection{The \glsentrydesc{LRM}}
\label{sec:lrmhinf:LRM}
The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:lrmhinf:sysDeltaFiniteDataFD} are smooth functions of the frequency.
As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
\begin{align}
  \Delta(\omega_{k+r})     
    &\approx 
        \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
      = 
        \frac{B_k(r)}{A_k(r)} 
      \isdef 
        \LocalModel{\Delta}_{k}(\omega_{k+r})
      \label{eq:lrmhinf:LRMTaylorSystem} \\
  T_{\Delta}(\omega_{k+r}) 
    &\approx 
        \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
      = 
        \frac{T_k'(r)}{A_k(r)} 
      \isdef 
        \LocalModel{T}_{k}(\omega_{k+r})
  \label{eq:lrmhinf:LRMTaylorTransient}
  \text{.}
\end{align}
Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \Set{-N_W,\ldots,+N_W}$ around each bin $k$.
This yields
\begin{equation}
  Y_{\Delta}(k+r) 
                 \approx
                    \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
                    + T_{\Delta}(\omega_{k+r}) 
    \quad
    \forall r \in \LocalWindow
    \text{.}
    \label{eq:lrmhinf:LocalWindowSpectra}
\end{equation}
By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
\begin{align}
  Y_{\Delta}(k+r) 
                  & \approx
                    \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
                    + \LocalModel{T}_k(\omega_{k+r}) 
                    & \forall r \in \LocalWindow \\
                  & = 
                    \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
                    + 
                    \frac{T'_k(r)}{A_k(r)} 
                    & \forall r \in \LocalWindow
    \text{.}
    \label{eq:lrmhinf:LocalWindowSpectraLRM}
\end{align}
To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
By doing so, the local linear-least-squares cost function
\begin{equation}
  \sum_{r=-N_W}^{N_W} 
  \left| 
    A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
  \right|^2
  \label{eq:lrmhinf:localCostLRM}
\end{equation}
 around each bin $k$ can be constructed.
We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.

For a more detailed overview of  the \gls{LPM} and \gls{LRM} see~\citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} and \chapref{sec:nonparametric}.

\section{Simulation}
\label{sec:lrmhinf:simulation}
To allow the generalization of the results of the simulations, we first introduce a way to decompose complex systems into simpler systems.
The behavior of these simpler systems then allows to predict the behavior for these more complex systems.
Concretely, any proper real-rational system $\Delta$ can be decomposed in a parallel connection of lower-order sub-systems by means of a partial fraction expansion as in \eqref{eq:excitation:PFE}, i.e.
\begin{equation}
\Delta(s) = 
         \deemph{
         \sum_{i=1}^{I_1} 
          \sum_{\multiplicity=1}^{M_{1,i}} 
            \frac{\dc[i]}
                      { \left( s - \pole[i] \right)^{\multiplicity}}
            + 
        }
        \sum_{i=1}^{I_2} 
          \deemph{\sum_{\multiplicity=1}^{M_{2,i}}}
           \frac{\dc[i,\multiplicity] \wn[i]^{2\multiplicity} \left( s + \wz[i] \right)}
                     {\wz[i] \left(s^2 + 2 \damping[i] \wn[i] s + \wn[i]^2 \right)^{\multiplicity}}
\end{equation}
with the same notations as in \chapref{sec:excitation}, most importantly, each resonant pole can be characterized by its frequency $\wn[i]$ and damping $\damping[i]$.
In the structural engineering community (see e.g. \citet[Chapter 2]{Gawronski2004}) it is well-known that around sharp resonance peaks ($\omega \approx \wn[i]$), the shape of a structural transfer function is mainly determined by its modal transfer function: the gray terms in the equation above are negligible such that only a single second-order term needs to be accounted for.
As a result, systems can often be well-represented, in a small frequency range, by a sum of a few low-order sub-systems (often first or second order for e.g. mechanical systems)~\citep[Section 2.2.2]{Gawronski2004}.
To estimate $\infnorm{\Delta}$ mainly the resonant sub-systems are of interest as those are responsible for large gains of the system.
Assuming such resonances are sufficiently separated in the frequency,~\citep{Schoukens2013LPMerror,Geerardyn2013TIM,Gawronski2004} show that results for a single resonance are applicable to more complex systems.
This is done by considering only the dominant resonance -- \emph{viz.} the one that is the most relevant for the $\Hinf{}$ controller design.
By normalizing the conclusions for the time constant $\timeconst$ (or the $3\unit{dB}$ bandwidth), the results are generally valid for different values of the damping $\damping$.
Specifically, the system's $\timeconst \isdef (\damping \wn)^{-1}$ dictates the required measurement time~\citep{Schoukens2013LPMerror}, where $\damping$ is the relative damping and $\wn$ the natural frequency of the dominant pole.

\subsection{A concrete simulation}
Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
\begin{equation}
  \Delta(z) 
    =  \frac{0.45373 z + 0.44752}
            {z^2 - 1.0595 z + 0.96079}
  \label{eq:lrmhinf:O2sysDT}
  \text{,}
\end{equation}
which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
\begin{equation}
  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
              {\sqrt{\inv{N}\sum_n v^2(n) }}
       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
  \label{eq:lrmhinf:SNR}
\end{equation}
of $10$ is obtained.

Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
In this chapter a Hann window and $N_S=1$ are used.
Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).

\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($N_B=1$). 
Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/example-both.tikz}
  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
  Hence, $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
  \label{fig:lrmhinf:exampleIntergrid}
\end{figure}

It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
The \gls{LPM}, on the other hand, does not provide a reliable estimate.
This behavior is related to the Runge phenomenon~\citep{Runge1901}.

\subsection{Study of the experiment length}
Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.

We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/MC-runlength.tikz}
  %\input{figures/runLength.tikz}
  \caption[Estimated $\gamma$ versus measurement time.]{The $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
  However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$). A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:lrmhinf:exampleIntergrid}. The shaded areas show the $\pm \sigma$ intervals which are due to the noise.
  }
\label{fig:lrmhinf:MC-run-length}
\end{figure}

It can be seen in \figref{fig:lrmhinf:MC-run-length} that $N \geq 20\timeconst$ is required to attain a frequency grid that is dense enough to obtain a reliable $\gammaAtGrid$, i.e. $\expectedValue{\gammaAtGrid} \approx \gamma$.
Starting from about $N=4 \text{ to } 5\timeconst$, the interpolated \gls{LRM} starts to yield good estimates for $\gammaIntergrid$.
For long experiments $(N \to \infty)$, the true $\infnorm{\Delta}$ is recovered.
Practically, this implies that the interpolated \gls{LRM} beats the on-grid estimate using a data record that is only a fraction of the length.

\begin{remark} \label{rem:lrmhinf:constructWeights}
The construction of weighting filters $(W,V)$ for the design of a robust controller typically happens based on measurement data which is available non-parametrically, i.e. only available at a limited frequency grid.
The goal of the filter design is to construct low-order minimum-phase filters that form a tight overbound of particular real-valued functions of the frequency.
Concretely, such a real-valued function is often a singular value of e.g. the loop gain or one of the loop sensitivity functions~\citep{Boeren2013,Scheid1995,Bibel1992,Skogestad2005} such that the design entails practical control objectives (disturbance rejection, input tracking, \ldots).
However, since such a function is only measured at a limited amount of frequency points, such overbounds can be hard to construct when resonances are present.
E.g. \citet{Scheid1995} describes a method to produce parametric overbounds, but note in Section~IV that limited frequency resolution can hamper construction of these filters.
The obvious solution to collect more densely-sampled data, is often not desirable (e.g. due to time constraints, limited access to the actual plant, cost of experimentation, \ldots).
However, the method proposed  in this chapter can provide more densely-sampled view of the data without an increase in measurement time.
\end{remark}

\begin{guideline}[Measure $4$ to $5\timeconst$ to observe its peak value using the local models]
After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
\end{guideline}

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts, that is free to move in six degrees of freedom.
Six geophones measure the payload velocity and eight linear motors allow to actively compensate for vibration of the platform.
To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.

\subsection{Measurement \& control framework}
\label{sec:lrmhinf:control}
The experiments on the \gls{AVIS} are carried out in closed-loop (\figref{fig:lrmhinf:tpc}) with $r_2 = 0$.
The controller $\Controller=\experimental\Controller$ is a diagonal \gls{PI} regulator which stabilizes the \gls{AVIS} but yields only moderate vibration isolation.
See \appref{app:avis-setup} for detailed information regarding both the experimental setup and the experimental controller.
The $r_1$ input consists of five periods of a random phase multisine of $65\,536$ samples with excited bins such that $\omega_k \approx 1.001 \omega_{k-1}$  and $\Ts=1\unit{ms}$.
See \chapref{sec:excitation} and \citep{Geerardyn2013TIM} for more information regarding the design of such a signal.

\begin{figure}
 \centering
 \input{\thisDir/figs/tpcrobust.tikz}
 \caption[Closed-loop block schematic.]{The considered feedback configuration $\ClosedLoop{\ModelSet[],\Controller}$.}
 \label{fig:lrmhinf:tpc}
\end{figure}

\begin{figure}
 \centering
 \input{\thisDir/figs/dualYoula.tikz}
 \caption[Dual-Youla parametrization.]{Dual-Youla parametrization of the closed-loop set-up  with controller $\Controller$,  model set $\ModelSet[]$ and nominal plant model $\estimated\Plant$.}
\label{fig:lrmhinf:dualYoula}
\end{figure}
